---
title: "Data Visualization Notes"
author: "<YOUR NAME HERE>"
date: "April 2023"
output: html_document
---


This document is part of the RStudio project containing slides and code for our data visualization workshop. 

## This Document is an RMarkdown File

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>. It lets you do two things. (1) It's a way of writing in plain text but with a few formatting instructions for marking up e.g. **bold** or *italic* text. (2) It allows you to alternate between passages of prose, like this, and "chunks" of R code that can be processed by RStudio. By marking up the plain text and processing the code, you can turn a plain-text document containing R Code into a formatted document containing the output of that code.  

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. A *code chunk* is a specially delimited section of the file. You can add one by moving the cursor to a blank line choosing Code > Insert Chunk from the RStudio menu. When you do, an empty chunk will appear in your file.

```{r }

```

Code chunks are delimited by three backticks (found to the left of the 1 key on US and UK keyboards) at the start and end. The opening backticks also have a pair of braces and the letter `r`, to indicate what language the chunk is written in. You write your code inside the code chunks. Write your notes and other material around them, as here. 

## Load Packages

To begin, we must load some packages we will be using. If we do not load them, R will not be able to find the functions contained in these libraries. Think of these packages like books in a library or tools in a toolkit. You have to install them once (as you might acquire a book for your library or acquire a tool for your workshop). Then, for each work session---like this one---you load them into your workspace (as you might take a book off a shelf or put a tool on a workbench) .

The `tidyverse` package includes `ggplot` and other tools. We also load the `socviz`, `here`, and `gapminder` packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

library(gapminder)
library(here)
library(socviz)
```

